Methodology for Assessing the State of the Practice for Domain X

### 2020-04-13 StateOfPractice/Methodology/Methodology.tex
Revert "update Methodology"
This reverts commit 71dc42cc24a9df57377a1b5d1579554b50ecfb42.

\usepackage{natbib}
\usepackage{booktabs}
\usepackage{amsmath,amsthm}

@@

@@

>>>>

\usepackage{natbib}
\usepackage{booktabs}
\usepackage{amsmath,amsthm}
\usepackage{hyperref}

@@

\begin{enumerate}
	\item Must be open source.
	\item Must have GitHub repository.
\end{enumerate}

@@

Commonality analysis document Steps:
\begin{enumerate}
	\item Introduction
	\item Overview of Domain
	\item Add Commonalities - Split into simulation, input, output, and nonfunctional requirements
	\item Add Variabilites - Split into simulation, input, output, system constraints, and nonfunctional requirements
	\item Add Parameters of Variation - Split into simulation, input, output, system constraints, and nonfunctional requirements
	\item Add Terminology, Definitions, Acronyms
\end{enumerate}

Commonality analysis for Lattice Boltzmann Solvers can be found \href{run:../Peter-Notes/Commonality-Analysis-LB-Systems.pdf}{here}.
